Adopting agile in the large: motivations, success factors and challenges

### 2014-05-16 journal/article.tex
Challenges: introductory paragraphs

@@

Any organizational transformation involving numerous individuals will face some
challenges. As stated by Research Question 3, we investigated what challenges
large organizations introducing agile methods may face.

The challenges presented in this section are factors that primary studies
described hindering the progress of the transformation.
Some of the challenges presented here were not explicitly presented as
transformation challenges, but rather as general difficulties in agile
imlementation. These issues are still included as creating an agile
implementation can be seen as a part of the transformation process.
Some solutions for challenges are also presented, but they should be considered
as ways of describing the challenges rather than direct success factors.

@@

Challenges can be organized on a high level into three categories. First we
discuss challenges relating to managing the transformation. These challenges
relate to managing people and resourcing. Secondly we present challenges in
choosing and establishing a suitable agile model. Thirdly challenges related to
large organization size are presented. Size will bring challenges such as
coordinating work between many teams and adapting other functions than
development to agile.

% Change resistance
% Lack of investment in transformation
% Agile is found to be hard
% Large organization issues
% Coordinating work between many teams
% Integrating other functions than development to agile
% Integrating requirements management and quality assurance
% Other challenges in transformation (zealots, falling back)

@@

@@

>>>>

\subsubsection{Typical activities in the transformation}

Training

Use of external consultants

Coaching

Pilot program

Seminars, workshops, other public events

Agile community

@@

Any organizational transformation that involves numerous individuals will face
some challenges. As stated by Research Question 3, we investigated what
challenges large organizations introducing agile methods may face.

The challenges presented in this section are factors that primary studies
described hindering the progress of the transformation. Some of the challenges
presented here do not explicitly relate to the transformation process, but are
rather general difficulties in agile imlementation. These issues are still
included as settling the agile implementation can be seen as a part of the
transformation process. Some solutions for challenges are also presented, but
they should be considered as ways of describing the challenges rather than
direct success factors.

@@

The challenges found in the primary studies are summarized in figure
\ref{fig:challenges_summary}. The challenges are organized on a high level into
seven categories within three themes. The categories are discussed subsequently
in this section. First we present generic transformation issues that may apply
to any organization. As the second theme challenges relating particularly to
sizable organizations are discussed. The final theme studied is challenges
encountered when agile development needs to interface with other functions
involved in a system development life cycle.

It is to be noted that we do not emphasize any of the listed categories or
challenges above another. The challenge categories we present were found evenly
in the set of primary studies. We included only challenges that had been
mentioned in several studies, or were particularly emphasized in fewer studies.
Challenges with only sporadic mentionings were considered less significant and
were left out. There was no further evidence that any challenge would be more
significant than another.

@@

\subsection{Success factors in transformation}

Some success factors ...

@@

* The factors that are listed are the ones to discuss -- there may be other
  factors affecting transformation, but this study provides evidence that these
  are the most important ones. We included only challenges that are discussed in
  more than studies, which proves that some filtering has been done.

* System development life cycle ?? -- There are inevitably other areas than
  development of increments, even in an agile process
